\artus -- Framework for Event-based Data Analysis in High Energy Physics

### 2015-09-09 Core/doc/latex/paper.tex
list with substructure

\begin{figure}[p]
\centering \input{figures/analysis_steps}
\caption[Characteristics of an event-based analysis in high energy physics]{Characteristic of an event-based analysis in high energy physics. I/O intensive operations are done in highly parallel in the WLCG. The computing-intensive operations are only performed if really necessary. This means that selection steps are performed as early as possible.}
\label{figure_analysis_steps}
\end{figure}
\clearpage
\section{Requirements and Challenges for Analysis Software\label{section_artus_challenges}}
%define requirements based on previous section, following sections: describe how they are fullfilled
Based on the workflow described in the previous section, the following demands for an analyis framework arise:
\begin{itemize}
 \item High performance to cope with massive data amounts % -> C++, pipelines, only necessary producers
 \item Usable for different physics analyses % -> modular structure, producers
 \item Flexibility %TODO define need for different configurations in previous section
 \item Compatible with different data formats % -> data format defined outside (kappa)
 \item Easy to install, use and understand; also for programming newcomers % test analysis, tutorial, documentation(TODO)
 \item Possibility to include libraries and existing HEP code % -> C++ used
 \item Reliable and checked source code % -> Unit tests, code sharing
 \item Compatibility with different operating platforms/environments % standalone compile with make, integrated batch/GC functionality
\end{itemize}
The \artus design choices are fully based on these requirements.

>>>>

\begin{figure}[p]
\centering \input{figures/analysis_steps}
\caption[Characteristics of an event-based analysis in high energy physics]{Characteristic of an event-based analysis in high energy physics. I/O intensive operations are done in highly parallel in the WLCG. The computing-intensive operations are only performed if really necessary. This means that selection steps are performed as early as possible.}
\label{figure_analysis_steps}
\end{figure}
\clearpage
\section{Requirements and Challenges for Analysis Software\label{section_artus_challenges}}
%define requirements based on previous section, following sections: describe how they are fullfilled
Based on the workflow described in the previous section, the following demands for an analyis framework arise:
\begin{itemize}
 \item Performance
 \begin{itemize}
  \item High performance for fast turnaround cycles, even with large data amounts % -> C++, pipelines, only necessary producers
  \item Flexibility %TODO define need for different configurations in previous section
 \end{itemize}
 \item Maintainability
 \begin{itemize}
  \item Easy to install
  \item Readable and understandable, also for programming newcomers
  \item Compatibility with different operating platforms/environments % standalone compile with make, integrated batch/GC functionality
  \item Compatible with different data formats % -> data format defined outside (kappa)
  \item Clear separation of code, data and settings % -> json config
 \end{itemize}

 \item Reliability
 \begin{itemize}
  \item Use existing libraries and existing HEP code wherever possible % -> C++ used
  \item Reliable and checked source code % -> Unit tests, code sharing
  \item Avoids frequent re-implementations by being used in different physics analyses % -> modular structure, producers
  \item Readable, since sourcecode is the most precise documentation possible
 \end{itemize}
\end{itemize}

The \artus design choices are fully based on these requirements.
